%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Latter Template
% LaTeX Template
%
% Original author:
% Oscar Neiva E. Neto (oscar-neiva.github.io)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{report} %padrao letterpaper, 10pt
\usepackage[utf8]{inputenc}
\usepackage{amsfonts,amssymb,graphicx,enumerate}
\usepackage[centertags]{amsmath}
\usepackage[lmargin=3cm,rmargin=3cm,tmargin=3cm,bmargin=3cm]{geometry}
\usepackage{identfirst}
\usepackage{setspace,cite}
\doublespacing
\renewcommand{\bibname}{Bibliografia}
%\usepackage[portuguese]{babel}

\newenvironment{dem}[1][Demonstra\c c\~ao]{\textbf{#1:}\

}  {\hfill\rule{1ex}{1ex}}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\center{Cover Letter}}
\vspace{-1.3cm}
\subsection*{\center{\small{Oscar Neiva}}}

\vspace{1cm}

I am an graduated student in Information Technology at FAETERJ. During my course I worked as a software developer in C ++ in the Laboratory of Intelligent Systems and Robotics - SIRLab and I did a scientific internship at the National Laboratory for Scientific Computing - LNCC.

At the SIRLab I worked with a team of four people to create an autonomous robot soccer team to the competitions IEEE VERY Small Size Soccer. Among the several parts of the development of this project I worked on the modeling, research and development of the system and the controllers of these non holonomic mobile robots. My work in SIRLab was developed over 1 year and 9 months and in 2014 my team wins the fourth position in the LARC - Latin American Robotics Competition.

During my scientific internship in LNCC I had worked with some concepts of stochastic systems, Markov chains, linear systems and other issues in the area of systems and control. At the end of the work I did a simulation in Matlab of the PageRank algorithm, the one responsible for making the Google search engine page rank. My work in LNCC was developed over 1 year and 11 months and was awarded with the prize "Featured in Scientific Initiation Day".

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}  
